A new tidy data structure to support exploration and modeling of temporal data

### 2019-08-30 tsibble.Rmd
final tweaks

Multiple time series, with each column corresponding to a measurement is tidy data when the time index is explicitly stored in a column. The stacked data format used in longitudinal data storage is tidy, and accommodates explicit identification of sub-groups.

@@

Index is an explicit data variable rather than a masked attribute (such as in the `ts` and `zoo` classes), exposing a need for more accessible and transparent time operations. It is often necessary to visualize and model seasonal effects of measurements of interest, meaning that time components, such as time of day and day of week, should be easily extracted from the index. When the index is available only as meta information, it provides an obstacle for analysts by complicating the writing of even simple queries, often requiring special purpose programming. From an analytical point of view this should be discouraged.

@@

There are three possible interval types: a number, unknown, and irregular. To determine the interval for regularly spaced data, tsibble computes the greatest common divisor, and is a number. If only one observation is available for each unit, which may occur after aggregating data, the interval is reported as unknown. When the data arrives with irregular time, like event data, the interval would be specified as irregular, to prevent the tsibble creator attempting to guess an interval.

@@

The **tsibble** package not only provides a tsibble data object but also a domain specific language in R for transforming temporal data. It takes advantage of the wrangling verbs implemented in the **dplyr** package, and develops a suite of new tools for facilitating temporal manipulation for easing, primarily, two aspects: implicit missingness handlers and time-aware aggregations.

>>>>

Multiple time series, with each column corresponding to a measurement is tidy data when the time index is explicitly stored in a column. The stacked data format used in longitudinal data is tidy, and accommodates explicit identification of sub-groups.

@@

Index is an explicit data variable rather than a masked attribute (such as in the `ts` and `zoo` classes), exposing a need for more accessible and transparent time operations. It is often necessary to visualize and model seasonal effects of measurements of interest, meaning that time components, such as time of day and day of week, should be easily extracted from the index. When the index is available only as meta information, it creates an obstacle for analysts by complicating the writing of even simple queries, often requiring special purpose programming. From an analytical point of view this should be discouraged.

@@

There are three possible interval types: fixed, unknown, and irregular. To determine the interval for regularly spaced data, tsibble computes the greatest common divisor as a fixed interval. If only one observation is available for each unit, which may occur after aggregating data, the interval is reported as unknown. When the data arrives with irregular time, like event data, the interval would be specified as irregular, to prevent the tsibble creator attempting to guess an interval.

@@

The **tsibble** package not only provides a tsibble data object but also a domain specific language in R for transforming temporal data. It takes advantage of the wrangling verbs implemented in the **dplyr** package, and develops a suite of new tools for facilitating temporal manipulation for primarily easing two aspects: implicit missingness handlers and time-aware aggregations.
